---
title: "16S_Nvec_10272019"
author: "Anthony_Bonacolta"
date: "10/20/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, include=FALSE, echo=FALSE}
library("phyloseq"); packageVersion("phyloseq")
library("ggplot2"); packageVersion("ggplot2")
library("ape"); packageVersion("ape")
library("vegan"); packageVersion("vegan")
library("dplyr")
library("scales")
library("grid")
library("reshape2")
library("edgeR")
library("plyr")
library("tidyr")
library("viridis")
library("DESeq2")
library("gridExtra")
```
# Load Data into Phyloseq
```{r,echo=FALSE}
SV <- read.table("/Users/anthonybonacolta/Box/Nvec_Microbiome/R_data/feature-tableNvec_new.txt", row.names = 1, header = TRUE)
tax <-as.matrix(read.table("/Users/anthonybonacolta/Box/Nvec_Microbiome/R_data/tax-no-MitoChNvec_ps_new.txt", row.names = 1, header = FALSE, sep = "\t"))
tree_file <-read_tree("/Users/anthonybonacolta/Box/Nvec_Microbiome/R_data/tree.nwk")
colnames(tax) <- c ("Kingdom", "Phylum", "Class", "Order", "Family", "Genus", "Species")
tax[tax==""] <- NA
map <- read.table("/Users/anthonybonacolta/Box/Nvec_Microbiome/R_data/16S_metadata_tab_phyloseq_new.txt", sep ="\t", row.names = 1, header = TRUE)
ps = phyloseq(otu_table(SV, taxa_are_rows=TRUE), 
               sample_data(map), 
               tax_table(tax),
                 phy_tree(tree_file))
ps
```
# PCoA Plots
```{r, echo=FALSE, warning=FALSE, message = FALSE}
ord.PCoA.brayP <- ordinate(ps, method="PCoA", distance="bray")
plot_ordination(ps, ord.PCoA.brayP, color="Tissue", label = "Sample")
PCoATissueWneg <- plot_ordination(ps, ord.PCoA.brayP, color="Tissue", label = "Sample")
svg(filename="/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/PCoATissue.svg")
plot(PCoATissueWneg)
dev.off()
```
# Species Richness
```{r, echo=FALSE, warning=FALSE, message = FALSE}
plot_richness(ps, x="Tissue", color="Tissue",
              measures=c("Simpson", "Shannon")) + geom_point()
richness <- plot_richness(ps, x="Tissue", color="Tissue",
              measures=c("Simpson", "Shannon")) + geom_point()
svg(filename="/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/richness.svg")
plot(richness)
dev.off()
jpeg(filename="/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/richness.jpeg")
plot(richness)
dev.off()
```

# Abundance Figures
## Phylum Level
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Nvec_phylum <- ps %>%
  tax_glom(taxrank = "Phylum") %>%                     # agglomerate at phylum level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.02) %>%                         # Filter out low abundance taxa
  arrange(Phylum)  
phylum_colors <- c(
  "#CBD588", "#5F7FC7", "orange","#DA5724", "#508578", "#CD9BCD",
   "#AD6F3B", "#673770","#D14285", "#652926", "#C84248", 
  "#8569D5", "#5E738F","#D1A33D", "#8A7C64", "#599861"
)

Tissue.labs <- c("Capitulum", "Mesenteries", "Physa")
names(Tissue.labs) <- c("capitulum", "mesenteries", "physa")


ggplot(Nvec_phylum, aes(x = Individual, y = Abundance, fill = Phylum)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = phylum_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Phyla > 2%) \n") +
  ggtitle("Phylum Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

```
```{r, echo=FALSE, include=FALSE, warning=FALSE, message = FALSE}
Phylum_comp <- ggplot(Nvec_phylum, aes(x = Individual, y = Abundance, fill = Phylum)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = phylum_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Phyla > 2%) \n") +
  ggtitle("Phylum Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Phylum_comp.tiff", units="in", width=5, height=5, res=300)
plot(Phylum_comp)
dev.off()
```
## Class
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Nvec_class <- ps%>%
  tax_glom(taxrank = "Class") %>%                     # agglomerate at phylum level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.02) %>%                         # Filter out low abundance taxa
  arrange(Class) 

class_colors <- c(
  "#CBD588", "#5F7FC7", "orange","#DA5724", "#508578", "#CD9BCD",
   "#AD6F3B", "#673770","#D14285", "#652926", "#C84248", 
  "#8569D5", "#5E738F","#D1A33D", "#8A7C64", "#599861"
)
ggplot(Nvec_class, aes(x = Individual, y = Abundance, fill = Class)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = class_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Class > 2%) \n") +
  ggtitle("Class Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")
```
```{r, echo=FALSE, include=FALSE, warning=FALSE, message = FALSE}
Class_comp <- ggplot(Nvec_class, aes(x = Individual, y = Abundance, fill = Class)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = class_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Class > 2%) \n") +
  ggtitle("Class Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Class_comp.tiff", units="in", width=5, height=5, res=300)
plot(Class_comp)
dev.off()
```
## Order
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Nvec_order <- ps %>%
  tax_glom(taxrank = "Order") %>%                     # agglomerate at phylum level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.02) %>%                         # Filter out low abundance taxa
  arrange(Order) 
Order_colors <- c(
  "#CBD588", "#5F7FC7", "orange","#DA5724", "#508578", "#CD9BCD",
   "#AD6F3B", "#673770","#D14285", "#652926", "#C84248", 
  "#8569D5", "#5E738F","#D1A33D", "#8A7C64", "#599861", "chocolate1", "beige", "coral", "blue", "purple"
)
ggplot(Nvec_order, aes(x = Individual, y = Abundance, fill = Order)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = Order_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Order > 2%) \n") +
  ggtitle("Order Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

```
```{r, echo=FALSE, include=FALSE, warning=FALSE, message = FALSE}
Order_comp <- ggplot(Nvec_order, aes(x = Individual, y = Abundance, fill = Order)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = Order_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Order > 2%) \n") +
  ggtitle("Order Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Order_comp.tiff", units="in", width=7, height=5, res=300)
plot(Order_comp)
dev.off()
```
## Family
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Nvec_Family <- ps %>%
  tax_glom(taxrank = "Family") %>%                     # agglomerate at phylum level
  transform_sample_counts(function(x) {x/sum(x)} ) %>% # Transform to rel. abundance
  psmelt() %>%                                         # Melt to long format
  filter(Abundance > 0.05) %>%                         # Filter out low abundance taxa
  arrange(Family) 
Family_colors <- c(
  "#CBD588", "#5F7FC7", "orange","#DA5724", "#508578", "#CD9BCD",
   "#AD6F3B", "#673770","#D14285", "#652926", "#C84248", 
  "#8569D5", "#5E738F","#D1A33D", "#8A7C64", "#599861", "chocolate1", "beige", "coral", "cyan1", "purple"
)
ggplot(Nvec_Family, aes(x = Individual, y = Abundance, fill = Family)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = Family_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Family > 5%) \n") +
  ggtitle("Family Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

```
```{r, echo=FALSE, include=FALSE, warning=FALSE}
Family_comp <- ggplot(Nvec_Family, aes(x = Individual, y = Abundance, fill = Family)) + 
  facet_grid(Tissue~., labeller = labeller(Tissue = Tissue.labs)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = Family_colors) +
  scale_x_discrete(
    breaks = c("1", "2", "3", "4", "5", "6"),
    labels = c("1", "2", "3", "4", "5", "6"), 
    drop = FALSE
  ) +
  # Remove x axis title
  xlab("Individual") +
  #
  guides(fill = guide_legend(reverse = TRUE, keywidth = 1, keyheight = 1)) +
  ylab("Relative Abundance (Family > 5%) \n") +
  ggtitle("Family Composition of Nematostella vectensis \n Bacterial Communities by Tissue Compartment")

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Family_comp.tiff", units="in", width=7, height=5, res=300)
plot(Family_comp)
dev.off()
```
# Fixed PCoA
```{r, echo=FALSE, warning=FALSE, message = FALSE}
sample_data(ps)$Individual <- factor(
  sample_data(ps)$Individual, 
  levels = c("1", "2", "3", "4", "5", "6")
)
Nvec_pcoa <- ordinate(
  physeq = ps, 
  method = "PCoA", 
  distance = "bray"
)

plot_ordination(
  physeq = ps,
  ordination = Nvec_pcoa,
  color = "Individual",
  shape = "Tissue",
  title = "PCoA of Nematostella vectensis Bacterial Communities"
) + 
  scale_color_manual(values = c("#a65628", "red", "#ffae19",
    "#4daf4a", "#1919ff", "darkorchid3", "magenta")
  ) +
  geom_point(aes(color = Individual), alpha = 0.7, size = 4) +
  geom_point(colour = "grey90", size = 1.5) 
```
```{r, echo=FALSE, warning=FALSE, message = FALSE}
BrayPCoA_NVec <- plot_ordination(
  physeq = ps,
  ordination = Nvec_pcoa,
  color = "Individual",
  shape = "Tissue",
  title = "PCoA of Nematostella vectensis Bacterial Communities"
) + 
  scale_color_manual(values = c("#a65628", "red", "#ffae19",
    "#4daf4a", "#1919ff", "darkorchid3", "magenta")
  ) +
  geom_point(aes(color = Individual), alpha = 0.7, size = 4) +
  geom_point(colour = "grey90", size = 1.5) 
svg(filename="/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/BrayPCoA_NVec.svg")
plot(BrayPCoA_NVec)
dev.off()
png(filename="/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/BrayPCoA_NVec.png")
plot(BrayPCoA_NVec)
dev.off()
```

## PERMANOVA
```{r, echo=FALSE, warning=FALSE}
Nvec_bray <- phyloseq::distance(ps, method = "bray")

# make a data frame from the sample_data
sampledf <- data.frame(sample_data(ps))

# Adonis test
adonis(Nvec_bray ~ Tissue, data = sampledf)

```
## Pie Charts
```{r, echo=FALSE, include=FALSE, warning=FALSE, message = FALSE}
phyla_counts_tab <- otu_table(tax_glom(ps, taxrank="Phylum")) 
phyla_tax_vec <- as.vector(tax_table(tax_glom(ps, taxrank="Phylum"))[,2]) 
rownames(phyla_counts_tab) <- as.vector(phyla_tax_vec)
unclassified_tax_counts <- colSums(SV) - colSums(phyla_counts_tab)
phyla_and_unidentified_counts_tab <- rbind(phyla_counts_tab, "Unclassified"=unclassified_tax_counts)
temp_major_taxa_counts_tab <- phyla_and_unidentified_counts_tab[!row.names(phyla_and_unidentified_counts_tab) %in% "Proteobacteria", ]
class_counts_tab <- otu_table(tax_glom(ps, taxrank="Class"))
class_tax_phy_tab <- tax_table(tax_glom(ps, taxrank="Class"))
phy_tmp_vec <- class_tax_phy_tab[,2]
class_tmp_vec <- class_tax_phy_tab[,3]
rows_tmp <- row.names(class_tax_phy_tab)
class_tax_tab <- data.frame("Phylum"=phy_tmp_vec, "Class"=class_tmp_vec, row.names = rows_tmp)
proteo_classes_vec <- as.vector(class_tax_tab[class_tax_tab$Phylum == "Proteobacteria", "Class"])
rownames(class_counts_tab) <- as.vector(class_tax_tab$Class) 
proteo_class_counts_tab <- class_counts_tab[row.names(class_counts_tab) %in% proteo_classes_vec, ]
proteo_no_class_annotated_counts <- phyla_and_unidentified_counts_tab[row.names(phyla_and_unidentified_counts_tab) %in% "Proteobacteria", ] - colSums(proteo_class_counts_tab)
major_taxa_counts_tab <- rbind(temp_major_taxa_counts_tab, proteo_class_counts_tab, "Unresolved_Proteobacteria"=proteo_no_class_annotated_counts)
identical(colSums(major_taxa_counts_tab), colSums(SV))
major_taxa_proportions_tab <- apply(major_taxa_counts_tab, 2, function(x) x/sum(x)*100)
dim(major_taxa_proportions_tab)
temp_filt_major_taxa_proportions_tab <- data.frame(major_taxa_proportions_tab[apply(major_taxa_proportions_tab, 1, max) > 5, ])
dim(temp_filt_major_taxa_proportions_tab) 
filtered_proportions <- colSums(major_taxa_proportions_tab) - colSums(temp_filt_major_taxa_proportions_tab)
filt_major_taxa_proportions_tab <- rbind(temp_filt_major_taxa_proportions_tab, "Other"=filtered_proportions)
filt_major_taxa_proportions_tab_for_plot <- filt_major_taxa_proportions_tab
filt_major_taxa_proportions_tab_for_plot$Major_Taxa <- row.names(filt_major_taxa_proportions_tab_for_plot)
filt_major_taxa_proportions_tab_for_plot.g <- gather(filt_major_taxa_proportions_tab_for_plot, Sample, Proportion, -Major_Taxa)
head(filt_major_taxa_proportions_tab_for_plot.g)
head(filt_major_taxa_proportions_tab_for_plot)
sample_info_for_merge<-data.frame("Sample"=map$ID, "Tissue"=map$Tissue, "Individual"=map$Individual, stringsAsFactors=F)
filt_major_taxa_proportions_tab_for_plot.g2 <- merge(filt_major_taxa_proportions_tab_for_plot.g, sample_info_for_merge)
```

## Capitulum
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Cap_sample_IDs <- row.names(map)[map$Tissue == "capitulum"]
filt_major_taxa_proportions_cap_only_tab_for_plot.g <- filt_major_taxa_proportions_tab_for_plot.g2[filt_major_taxa_proportions_tab_for_plot.g2$Sample %in% Cap_sample_IDs, ]
Cap_sample_major_taxa_proportion_tab <- acast(filt_major_taxa_proportions_cap_only_tab_for_plot.g[, c(1:3)], Major_Taxa ~ Sample)
Cap_sample_summed_major_taxa_proportions_vec <- rowSums(Cap_sample_major_taxa_proportion_tab)
Cap_sample_major_taxa_summary_tab <- data.frame("Major_Taxa"=names(Cap_sample_summed_major_taxa_proportions_vec), "Proportion"=Cap_sample_summed_major_taxa_proportions_vec, row.names=NULL)
ggplot(data.frame(Cap_sample_major_taxa_summary_tab), aes(x="Capitulum samples", y=Proportion, fill=Major_Taxa)) + 
  geom_bar(width=1, stat="identity") +
  coord_polar("y") +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("Capitulum") +
  theme_void() +
  theme(plot.title = element_text(hjust=0.5), legend.title=element_blank())
```
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Cap_pie <- ggplot(data.frame(Cap_sample_major_taxa_summary_tab), aes(x="Capitulum samples", y=Proportion, fill=Major_Taxa)) + 
  geom_bar(width=1, stat="identity") +
  coord_polar("y") +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("Capitulum") +
  theme_void() +
  theme(plot.title = element_text(hjust=0.5), legend.title=element_blank())

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Cap_pie.tiff", units="in", width=6, height=5, res=300)
plot(Cap_pie)
dev.off()
```

## Mesenteries
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Mes_sample_IDs <- row.names(map)[map$Tissue == "mesenteries"]
filt_major_taxa_proportions_mes_only_tab_for_plot.g <- filt_major_taxa_proportions_tab_for_plot.g2[filt_major_taxa_proportions_tab_for_plot.g2$Sample %in% Mes_sample_IDs, ]
Mes_sample_major_taxa_proportion_tab <- acast(filt_major_taxa_proportions_mes_only_tab_for_plot.g[, c(1:3)], Major_Taxa ~ Sample)
Mes_sample_summed_major_taxa_proportions_vec <- rowSums(Mes_sample_major_taxa_proportion_tab)
Mes_sample_major_taxa_summary_tab <- data.frame("Major_Taxa"=names(Mes_sample_summed_major_taxa_proportions_vec), "Proportion"=Mes_sample_summed_major_taxa_proportions_vec, row.names=NULL)
ggplot(data.frame(Mes_sample_major_taxa_summary_tab), aes(x="Mesentery samples", y=Proportion, fill=Major_Taxa)) + 
  geom_bar(width=1, stat="identity") +
  coord_polar("y") +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("Mesenteries") +
  theme_void() +
  theme(plot.title = element_text(hjust=0.5), legend.title=element_blank())
```
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Mes_pie <- ggplot(data.frame(Mes_sample_major_taxa_summary_tab), aes(x="Mesentery samples", y=Proportion, fill=Major_Taxa)) + 
  geom_bar(width=1, stat="identity") +
  coord_polar("y") +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("Mesenteries") +
  theme_void() +
  theme(plot.title = element_text(hjust=0.5), legend.title=element_blank())

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Mes_pie.tiff", units="in", width=6, height=5, res=300)
plot(Mes_pie)
dev.off()
```

## Physa
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Phy_sample_IDs <- row.names(map)[map$Tissue == "physa"]
filt_major_taxa_proportions_phy_only_tab_for_plot.g <- filt_major_taxa_proportions_tab_for_plot.g2[filt_major_taxa_proportions_tab_for_plot.g2$Sample %in% Phy_sample_IDs, ]
Phy_sample_major_taxa_proportion_tab <- acast(filt_major_taxa_proportions_phy_only_tab_for_plot.g[, c(1:3)], Major_Taxa ~ Sample)
Phy_sample_summed_major_taxa_proportions_vec <- rowSums(Phy_sample_major_taxa_proportion_tab)
Phy_sample_major_taxa_summary_tab <- data.frame("Major_Taxa"=names(Phy_sample_summed_major_taxa_proportions_vec), "Proportion"=Phy_sample_summed_major_taxa_proportions_vec, row.names=NULL)
ggplot(data.frame(Phy_sample_major_taxa_summary_tab), aes(x="Physa samples", y=Proportion, fill=Major_Taxa)) + 
  geom_bar(width=1, stat="identity") +
  coord_polar("y") +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("Physa") +
  theme_void() +
  theme(plot.title = element_text(hjust=0.5), legend.title=element_blank())
```
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Phy_pie <- ggplot(data.frame(Phy_sample_major_taxa_summary_tab), aes(x="Physa samples", y=Proportion, fill=Major_Taxa)) + 
  geom_bar(width=1, stat="identity") +
  coord_polar("y") +
  scale_fill_viridis(discrete=TRUE) +
  ggtitle("Physa") +
  theme_void() +
  theme(plot.title = element_text(hjust=0.5), legend.title=element_blank())

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Phy_pie.tiff", units="in", width=6, height=5, res=300)
plot(Phy_pie)
dev.off()
```
# Betadisperser
```{r, echo=FALSE, warning=FALSE}
DESeq_map <-read.table("/Users/anthonybonacolta/Box/Nvec_Microbiome/R_data/DESeq_map.txt", sep ="\t", row.names = 1, header = TRUE)
deseq_counts <- DESeqDataSetFromMatrix(SV[,-19], colData =DESeq_map, design = ~Tissue)
deseq_counts_vst <- varianceStabilizingTransformation(deseq_counts)
vst_trans_count_tab <- assay(deseq_counts_vst)
euc_dist <- dist(t(vst_trans_count_tab))
euc_clust <- hclust(euc_dist, method="ward.D2")
plot(euc_clust)
```
```{r}
anova(betadisper(euc_dist, map$Tissue))
adonis(euc_dist~map$Tissue)
```
## Visualize PERMANOVA
```{r, echo=FALSE}
vst_pcoa <- ordinate(ps, method="MDS", distance="euclidean")

plot_ordination(
  physeq = ps,
  ordination = vst_pcoa,
  color = "Individual",
  shape = "Tissue",
  title = "PCoA of Nematostella vectensis Bacterial Communities"
) + 
  scale_color_manual(values = c("#a65628", "red", "#ffae19",
    "#4daf4a", "#1919ff", "darkorchid3", "magenta")
  ) +
  geom_point(aes(color = Individual), alpha = 0.7, size = 4) +
  geom_point(colour = "grey90", size = 1.5) + 
  annotate("text", x=40000, y=40000, label="Tissue Regions") +
  annotate("text", x=40000, y=36000, label="Permutational ANOVA = 0.041*")

```
```{r, echo=FALSE}
PCoA_Euc <- plot_ordination(
  physeq = ps,
  ordination = vst_pcoa,
  color = "Individual",
  shape = "Tissue",
  title = "PCoA of Nematostella vectensis Bacterial Communities"
) + 
  scale_color_manual(values = c("#a65628", "red", "#ffae19",
    "#4daf4a", "#1919ff", "darkorchid3", "magenta")
  ) +
  geom_point(aes(color = Individual), alpha = 0.7, size = 4) +
  geom_point(colour = "grey90", size = 1.5) + 
  annotate("text", x=40000, y=40000, label="Tissue Regions") +
  annotate("text", x=40000, y=36000, label="Permutational ANOVA = 0.041*")

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/PCoA_Euc.tiff", units="in", width=7, height=5, res=300)
plot(PCoA_Euc)
dev.off()
```

# MicroBiomeSeq Analysis for Alpha and Beta Diversity Measures

```{r, echo=FALSE, warning=FALSE, message = FALSE, include=FALSE}
library(devtools)
library(phyloseq)
library(microbiomeSeq)
library(ggplot2)
physeq = ps
```

# Alpha Diversity with ANOVA (P<0.05)
```{r, echo=FALSE, warning=FALSE, message = FALSE}
Alpha_ANOVA <- plot_anova_diversity(physeq, method = c("richness", "simpson", "shannon"), 
    grouping_column = "Tissue", pValueCutoff = 0.05)
print(Alpha_ANOVA)

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/Alpha_ANOVA.tiff", units="in", width=7, height=5, res=300)
plot(Alpha_ANOVA)
dev.off()
```

## Differentially abundant taxa 
### Between Tissue compartmen, corresponding adjusted p-values and rank of importance as detected by random forest classifier.

```{r, echo=FALSE, warning=FALSE, message = FALSE, fig.width=5,fig.height=5}
physeq2 <- taxa_level(physeq, "Phylum")
deseq_sig <- differential_abundance(physeq2, grouping_column = "Tissue", output_norm = "log-relative", 
    pvalue.threshold = 0.05, lfc.threshold = 0, filename = F)
diff_Phy <- plot_signif(deseq_sig$plotdata, top.taxa = 5)
print(diff_Phy)

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/diff_Phy.tiff", units="in", width=7, height=8, res=300)
plot(diff_Phy)
dev.off()
```

#### Very little or no Lentisphaerae in Capitulum Samples

## Mean Decrease Accuracy
```{r, echo=FALSE, warning=FALSE, message = FALSE}
MDA <- plot_MDA(deseq_sig$importance)
print(MDA)

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/MDA.tiff", units="in", width=7, height=5, res=300)
plot(MDA)
dev.off()
```

### Factor in Abundance 
```{r, echo=FALSE, warning=FALSE, message = FALSE}
MA <- plot_MA(deseq_sig$SignFeaturesTable)
print(MA$lfcplot)

tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/MA.tiff", units="in", width=7, height=8, res=300)
plot(MA$lfcplot)
dev.off()
```
 
 
 **Down reg are more common in Cap, Up reg are more common in other compartments**
 
 
```{r}
library("ampvis2")
if(!require("devtools"))
  install.packages("devtools")
#source the phyloseq_to_ampvis2() function from the gist
devtools::source_gist("8d0ca4206a66be7ff6d76fc4ab8e66c6")
ampvis2_obj <- phyloseq_to_ampvis2(ps)
```
 
 
```{r}
hm <- amp_heatmap(ampvis2_obj, group_by = "Tissue", tax_aggregate = "Family", tax_show = 9)+theme_classic()+labs(title="Read Abundance for Top Bacterial Families", subtitle="Divided by Tissue Compartment")
tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/hm.tiff", units="in", width=8, height=5, res=300)
plot(hm)
dev.off()
```
 
```{r}
library(ALDEx2);
packageVersion("ALDEx2")
library(CoDaSeq)
packageVersion("CoDaSeq")

d.czm.all <- cmultRepl(SV[1:18], method="CZM", label=0)
d.clr.all <- codaSeq.clr(d.czm.all)
E.clr <- t(d.clr.all)
d.pcx <- prcomp(E.clr)

dist.clr <- dist(E.clr)
```
```{r}
tiss <- map$Tissue
ano <- anosim(dist.clr, tiss, permutations=9999)
ano
```
```{r}
plot(ano)
```
```{r}
df_out <- as.data.frame(d.pcx$x)
p<-ggplot(df_out,aes(x=PC1,y=PC2,fill=factor(map$Individual),shape=map$Tissue))
p<-p+geom_point(size=3, position=position_jitter(h=0.1, w=0.1))+
  scale_shape_manual(values=c(21,24,22), name = "Tissue") +scale_fill_viridis_d(option="magma", name = "Individual") +
  guides(fill = guide_legend(override.aes=list(shape=21))) + ggtitle("PCA of Nematostella vectensis Bacterial Communities") + annotate("text", x=35, y=75, label="Tissue ANOSIM = 0.1483 \n (9999 Permutations)") +theme_bw()
p

#tiff("/Users/anthonybonacolta/Box/Nvec_Microbiome/Figures/TIFF/PCA_Ait.tiff", units="in", width=7, height=5, res=300)
#plot(p)
#dev.off()
```

